Notes on two photon scattering of the molecular state

### 2019-11-25 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Do not specify what Rabi frequency we are calculating.
The calculation can be used in multiple cases so we can be generic about it.
Also tweak some footnote wording.

Assume the Raman Rabi frequency between the initial state and the ground motional state
is $\Omega_R$, the Raman Rabi frequency for another motional state would be,

\eqar{
  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
}

In order to calculate the coupling to the continuum, we'll start with a discrete set of states
and and then take the energy gap to $0$ to calculate the result for true continuum.
We'll use two different sets of states to calculate for cross-checking\footnote{
  Note that both calculations will be done under the same assumptions given above so their
  agreement does not necessarily mean that the assumption is valid.}.

@@

The Raman Rabi frequency to the motional state is therefore,
\eqar{
  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
  =&\Omega_R\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
  =&\Omega_R\paren{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}^{1/4}
}
The decay rate is
\eqar{
  \gamma=&\frac{2\pi\Omega_R'^2}{2\omega}\\
  =&\frac{\pi\Omega_R^2}{\omega}\sqrt{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}\\
  =&\Omega_R^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
}
where $E$ is the energy (in frequency unit) of the continuum energy we are coupling to.

>>>>

Assume the Rabi frequency between the state of interest and the ground motional state
is $\Omega$\footnote{This can be either a Raman Rabi frequency for ground state loss rate,
  or the up leg single photon Rabi frequency for the excited state broadening.},
the Rabi frequency for another motional state would be,

\eqar{
  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
}

In order to calculate the coupling to the continuum, we'll start with a discrete set of states
and and then take the energy gap to $0$ to calculate the result for true continuum.
We'll use two different sets of states to calculate for cross-checking\footnote{
  Note that both calculations will be done under the same assumptions given above so their
  agreement does not validate the assumption.}.

@@

The Rabi frequency to the motional state is therefore,
\eqar{
  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
  =&\Omega\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
  =&\Omega\paren{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}^{1/4}
}
The decay rate is
\eqar{
  \gamma=&\frac{2\pi\Omega'^2}{2\omega}\\
  =&\frac{\pi\Omega^2}{\omega}\sqrt{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}\\
  =&\Omega^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
}
where $E$ is the energy (in frequency unit) of the continuum energy we are coupling to.

\subsection{Spherical box}

We can also treat the continuum as the spectrum of a large spherical infinitely deep well
when the radius of the sphere $R$ is infinite.
The radial wavefunctions of the eigenstates are,

\eqar{
  u_n=&\sqrt{\frac{2}{R}}\sin\paren{\frac{\pi nr}{R}}
}

with energy\footnote{In frequency unit} $E=\dfrac{\pi^2\hbar n^2}{2mR^2}$.
Energy gap between neighboring state is $\Delta E\approx\dfrac{\pi^2\hbar n}{mR^2}$,

\eqar{
  \psi(r=0)=&\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}\\
  =&\frac{\pi n}{\sqrt{2\pi R}R}\\
  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
  =&\Omega\frac{\pi n}{\sqrt{2\pi R}R}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
}

The decay rate is
\eqar{
  \gamma=&\frac{2\pi\Omega'^2}{\Delta E}\\
  =&2\pi\Omega^2\frac{\pi^2 n^2}{2\pi R^3}\sqrt{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}\frac{mR^2}{\pi^2\hbar n}\\
  =&\Omega^2\frac{n}{R}\sqrt{\frac{\pi^3\hbar}{m\omega_1\omega_2\omega_3}}\\
  =&\Omega^2\frac{1}{R}\sqrt{\frac{\pi^3\hbar}{m\omega_1\omega_2\omega_3}\frac{2mR^2E}{\pi^2\hbar}}\\
  =&\Omega^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
}
Which is the same result we got using the harmonic oscillator states.
